\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{geometry}
\geometry{
textwidth=550pt,
textheight=700pt,
}
\usepackage{layout}


\pdfgentounicode=1
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\setlength{\footskip}{3.60004pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]
\setlist[itemize]{leftmargin=*}
\begin{document}

\begin{center}
	\textbf{\LARGE Eldon Stegall } \\
	\large
	Security, Reliability, Engineering Effectiveness \\
	\vspace{+3pt}
	\small
	\hspace{.5pt} \href{https://eldondev.com/github}{\color{blue}GitHub:eldondevat}
	\hspace{.5pt} \href{mailto:esrtxr@eldondev.com}{\color{blue}esrtxr@eldondev.com}
	\hspace{.5pt} \href{tel:+1-404-492-6299}{\color{blue}+1-404-492-6299}
\end{center}


\section{Goals and Successes}
\small
\newsavebox{\objbox}
\sbox{\objbox}{
	\begin{minipage}[b]{0.65\textwidth}
		To build a world with greater equality, freedom, and privacy for all, leveraging my \mbox{experience engineering} secure software systems.
		\begin{itemize}
			\setlength\itemsep{0.1em}
			\item Collaborated on the design and technical implementation of controls for a distributed team to operate internal systems for Fortune 500 enterprises, and enable new LOB.
			\item Worked with an international team to design and build an encrypted network for IOT security devices to communicate over LTE, enabling robust application responsiveness.
			\item Architected secure, authenticated cloud management of devices based on least-privileged roles to ease customer management and improve satisfaction.
			\item Mentored junior and mid-level engineers with clarity, empathy, and humility. Joyfully watched mentees move on to mentor others in the Atlanta Infosec Community.
			\item Managed external pentests and regular security audits as the sole Security Architect at a company with multiple international enterprise clients, satisfying meticulous customer security stakeholders.
		\end{itemize}
	\end{minipage}
}
\usebox{\objbox}\hfill
\fbox{
	\begin{minipage}[b]{0.3\textwidth}
		\small\raggedright
		Recent positions held, references and \\ comprehensive 18 year professional software history available on request.
		\begin{itemize}
			\item Keep Technologies, 2021 - 2023, Engineer
			\item Roadie, 2021, Senior Software Engineer
			\item DataStax, 2017 - 2020, \mbox{Security Architect}
			\item CodeGuard, 2015 - 2017, Senior Software Engineer
			\item Apalachee Software, 2013 - Present, Principal Consultant
		\end{itemize}
	\end{minipage}
}

\section{Recent Experience}
Enjoying the agility of startups, I have maintained a
career-long passion for effective collaboration in the service of security and efficiency in mission-oriented organizations.
\begin{itemize}
	\item Vulnerability management, incident response coordination, disaster recovery testing, SOC 2 controls design, and pentest management. \textbf{Security} \textit{DataStax, 2020}
	      \setlength\itemsep{0.1em} \item A comprehensive embedded firmware system
	      built with the Yocto toolkit. \textbf{Effective Engineering} \textit{Keep Technologies, 2023}
	\item A \textbf{Golang} IOT agent communicating securely via mTLS with AWS IOT, and integrating with a variety of cloud functionality for video processing, observability, and cloud control. \textbf{Security}, \textbf{Effective Engineering} \textit{Keep Technologies, 2022}
	\item A Terraform strategy for building and deploying per-endpoint AWS lambda functions, decreasing the time to deploy new API endpoints to less than a day, including per-endpoint monitoring and Authn/Authz. \textbf{Security}, \textbf{Reliability} \textit{Keep Technologies, 2021}
	\item Multiteam migration of microservices and databases from Heroku to EKS, including containerization and multi-environment operation. \textbf{Reliability} \textit{Roadie, 2021}
	\item A Kubernetes operator to deploy a distributed database, enabling TLS certificate provisioning to secure communications into and between nodes. \textbf{Security} \textit{DataStax, 2020}
\end{itemize}


\section{Technology Focus}
In order to deliver services to users, I typically use technology and tooling such as
\begin{itemize}
	\setlength\itemsep{0.1em}
	\item JIRA, Github Issues, or Shortcut to manage IT initiative tasks, track progress and estimate milestones.
	\item SOC 2 to check control implementations against best practices.
	\item GSuite or Okta to enable organization identity provisioning
	\item mTLS, Wireguard, Tailscale, or OpenVPN to manage network connectivity on zero-trust networks
	\item CIS Benchmarks and open-source conformance checkers such as Prowler to evaluate system security posture,
	\item \textbf{Golang},  \textbf{Python},  \textbf{Ruby}, or \textbf{Java} to impement software features.
	\item Github Actions, Gitlab Pipelines, or Jenkins to continuously check the security and operation of the deployed configurations,
	\item Kubernetes or Terraform to deploy software to a cloud provider in execution environments such as Lambda, EKS or GKE. I have also worked with operating Kubernetes as a platform on bare metal in production environments.
\end{itemize}

\section{Additional Topics, Accomplishments, And Efforts}
Adjacent to my daily work, I improve my craft and contribute back to the community in a variety of ways, including
\begin{itemize}
	\setlength\itemsep{0.1em}
	\item BSc Computer Science, BSc Discrete Mathematics, Ga Tech, 2006
	\item Presenting at BSides Atlanta 2020 as a remote speaker on \href{https://www.youtube.com/watch?v=kLCaAaUd1mM}{\color{blue}Cloud Security tooling}
	\item Deploying and maintaining the installation of Open Source video conferencing technology enabling remote meetings of the Atlanta Cybersecurity community facilitating presentations by numerous Cybersecurity professionals to the public.
	\item Presentation currently in review: \textbf{Device Security via delegated AWS Credentials}
	\item Contributing improvements and fixes to projects such as the AWS Terraform provider, Wireshark, and Qemu.
	\item Obtaining the Certified Kubernetes Administrator recognition from the Cloud Native Computing Foundation.
\end{itemize}
%\layout*
\end{document}

