
\documentclass[letterpaper]{letter}
\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}


\signature{Eldon Stegall}
\address{62 Spruce St NE\\ Atlanta, GA 30307}
\telephone{404-492-6299}

\begin{document}

\begin{letter}  {Rubin Observatory \\950 Cherry Ave. \\Tucson, AZ 85719}

\opening{Dear Sir or Madam,}

Hello, I am writing with regards to the position at Rubin Observatory providing
services around the data collected by the telescopes you operate. I initially
saw the post for this job on the y-combinator discussion board, and jumped at
the thought of workin on something which I feel is profoundly valuable to
humanity. I have spent the last 15 or so years doing the deeply technical
nitty-gritty work at startups (some in the Atlanta area, some fully remote). I
have, at times, created some great value for shareholders (of which I
occasionally was one).  The benefits for customers were greater data security
and reliability.  Now I would like to put the experience and passion to work
towards an effort which has the potential to inspire and excite anyone who can
look up at the sky and wonder about the distant bodies we observe there.

I have recently worked primarily in golang, but have built and maintained a
variety of python codebases, sometimes handling substantial datasets, including
jobs built on top of big data processing platforms including Hadoop and Spark,
processing data from systems such as Postgres, Object stores like GCS and
distributed databases such as Apache Cassandra. I have designed and implemented
APIs to serve synchronous queries, often leveraging OpenAPI, or streaming
workflows using AMQP or GRPC to process and surface data to teams doing data
science or end users. I have used Kubernetes both in cloud offerings such as
AWS and GKE, and on-prem.

I am opinionated and driven, and am intentionally seeking a team that is excited
about their work, creating something with meaning, and eager to share their wisdom
and share in the wisdom of others.

\closing{Thank you for your consideration,}

\end{letter}

\end{document}

